\thetitle

### 2022-06-30 thesis/paper.tex

\ifen
We refer to this problem as the \emph{optimal college application} problem, as follows. Consider an admissions market with $m$ colleges. The $j$th college is named $c_j$. Consider a single prospective student in this market, and let each $t_j$-value indicate the utility she associates with attending $c_j$, where her utility is $t_0$ if she does not attend college. Let $g_j$ denote the application fee for $c_j$ and $H$ the student's total budget to spend on application fees. Lastly, let $f_j$ denote the student's probability of being admitted to $c_j$ if she applies, so that $Z_j$ equals one if she is admitted and zero if not. It is appropriate to assume that the $Z_j$ are statistically independent as long as $f_j$ are probabilities estimated specifically for this student (as opposed to generic acceptance rates). Then the student's objective is to maximize the expected utility associated with the best school she gets into within this budget. Therefore, her optimal college application strategy is given by the solution $\mathcal{X}$ to the problem above, where $\mathcal{X}$ represents the set of schools to which she applies. 
\else
다음 해석에 따라 이를 `대학 입학 지원 최적화 문제'라고 부른다. $m$개의 대학교를 가지는 입학 시장을 고려하자. $j$번째 학교의 이름은 $c_j$다. 어떤 학생이 $c_j$에 입학하게 되면 효용 $t_j$를 얻게 된다고 하자. 단, 어떤 대학에도 진학하지 않는 경우 그 학생의 효용은 $t_0$이다. $c_j$의 지원 비용이 $g_j$이며 학생이 지원에 쓸 수 있는 예산이 $H$라고 하자. 마지막으로, $c_j$에 지원하면 학생이 합격할 확률이 $f_j$이라고 하자. 따라서 합격하면 $Z_j = 1$, 합격 안 하면 $Z_j = 0$이 된다. $f_j$가 (학교의 전체적인 합격률이 아니라) 바로 이 학생의 합격 확률일 때 $Z_j$의 확률적 독립성은 적절한 가정이다. 그러면 학생의 목표는 주어진 예산 안에서 학생이 합격하는 학교들에서 얻는 효용 중 기대 최댓값을 최대화하는 것이다. 위 문제의 최적해가 $\mathcal{X}$일 때, 학생의 최적 대학 지원 전략은 $\mathcal{X}$에  속한 학교로 지원하는 것이다.
\fi

@@

\ifen
Let $U_{\mathrm{max}} = \sum_{j \in \mathcal{B}} u_j$ and $\delta = {1} /{m U_{\mathrm{max}}} > 0$, and construct an instance of Ellis’s problem with $\mathcal{C} = \mathcal{B}$, $H = W$, all $f_j = \delta$, and each $t_j = u_j / \delta$. Clearly, $\mathcal{X} \subseteq \mathcal{C}$ is feasible for Ellis’s problem if and only if it is feasible for the knapsack instance. Now, we observe that for any nonempty $\mathcal{X}$,
\else
$U_{\mathrm{max}} = \sum_{j \in \mathcal{B}} u_j$와 $\delta = {1} /{m U_{\mathrm{max}}} > 0$일 때, $\mathcal{C} = \mathcal{B}$, $H = W$,  모든 $f_j = \delta$, 그리고 각 $t_j = u_j / \delta$인 엘리스 문제의 인스턴스를 고려하자. $\mathcal{X} \subseteq \mathcal{C}$가 엘리스 문제의 가능해가 되는 것은 배낭 문제 인스턴스의 가능해가 되는 것과 동치임을 쉽게 알 수 있다. 그러면 공집합이 아닌 임의의 $\mathcal{X}$ 에 대해,
\fi
\begin{align}
\begin{split}
\sum_{j \in \mathcal{X}} u_j &=  \sum_{j \in \mathcal{X}} f_j t_j
> \sum_{j \in \mathcal{X}} \Bigl( f_j t_j \prod_{\substack{j’ \in \mathcal{X}: \\ j' > j}} (1 - f_{j’}) \Bigr)
= v(\mathcal{X}) \\
&= \sum_{j \in \mathcal{X}} \Bigl( u_j  \prod_{\substack{j’ \in \mathcal{X}: \\ j' > j}} (1 - \delta) \Bigr)
\geq (1 - \delta)^m \sum_{j \in \mathcal{X}} u_j \\
&\geq (1 - m\delta) \sum_{j \in \mathcal{X}} u_j 
\geq \sum_{j \in \mathcal{X}} u_j  - m\delta U_{\mathrm{max}}
= \sum_{j \in \mathcal{X}} u_j  - 1.
\end{split}
\end{align}
\ifen
This means that the utility of an application portfolio $\mathcal{X}$ in the corresponding knapsack instance is the smallest integer greater than $v( \mathcal{X})$. That is, $\sum_{j \in \mathcal{X}} u_j \geq U$ if and only if $v(\mathcal{X}) \geq U -1$. Taking $V = U-1$ completes the transformation and concludes the proof. 
\else
이는 지원 포트폴리오 $\mathcal{X}$가 해당 배낭 문제에서 일으키는 효용이 $v( \mathcal{X})$보다 크면서 가장 작은 정수임을 의미한다. 즉, $\sum_{j \in \mathcal{X}} u_j \geq U$가 성립할 필요충분 조건은 $v(\mathcal{X}) \geq U -1$이다. $V = U-1$으로 정의하여 변환을 완성하면 증명이 완료된다.
\fi
\end{proof}

>>>>

\ifen
We refer to this problem as the \emph{optimal college application} problem, as follows. Consider an admissions market with $m$ colleges. The $j$th college is named $c_j$. Consider a single prospective student in this market, and let each $t_j$-value indicate the utility she associates with attending $c_j$, where her utility is $t_0$ if she does not attend college. Let $g_j$ denote the application fee for $c_j$ and $H$ the student's total budget to spend on application fees. Lastly, let $f_j$ denote the student's probability of being admitted to $c_j$ if she applies, so that $Z_j$ equals one if she is admitted and zero if not. It is appropriate to assume that the $Z_j$ are statistically independent as long as $f_j$ are probabilities estimated specifically for this student (as opposed to generic acceptance rates). Then the student's objective is to maximize the expected utility associated with the best school she is admitted to. Therefore, her optimal college application strategy is given by the solution $\mathcal{X}$ to the problem above, where $\mathcal{X}$ represents the set of schools to which she applies. 
\else
다음 해석에 따라 이를 `대학 입학 지원 최적화 문제'라고 부른다. $m$개의 대학교를 가지는 입학 시장을 고려하자. $j$번째 학교의 이름은 $c_j$다. 어떤 학생이 $c_j$에 입학하게 되면 효용 $t_j$를 얻게 된다고 하자. 단, 어떤 대학에도 진학하지 않는 경우 그 학생의 효용은 $t_0$이다. $c_j$의 지원 비용이 $g_j$이며 학생이 지원에 쓸 수 있는 예산이 $H$라고 하자. 마지막으로, $c_j$에 지원하면 학생이 합격할 확률이 $f_j$이라고 하자. 따라서 합격하면 $Z_j = 1$, 합격 안 하면 $Z_j = 0$이 된다. $f_j$가 (학교의 전체적인 합격률이 아니라) 바로 이 학생의 합격 확률일 때 $Z_j$의 확률적 독립성은 적절한 가정이다. 그러면 학생의 목표는 주어진 예산 안에서 학생이 합격하는 학교들에서 얻는 효용 중 기대 최댓값을 최대화하는 것이다. 위 문제의 최적해가 $\mathcal{X}$일 때, 학생의 최적 대학 지원 전략은 $\mathcal{X}$에  속한 학교로 지원하는 것이다.
\fi

@@

\ifen
Let $U_{\mathrm{max}} = \sum_{j \in \mathcal{B}} u_j$ and $\delta = {1} /{m U_{\mathrm{max}}} \in (0, 1)$, and construct an instance of Ellis’s problem with $\mathcal{C} = \mathcal{B}$, $H = W$, all $f_j = \delta$, and each $t_j = u_j / \delta$. Clearly, $\mathcal{X} \subseteq \mathcal{C}$ is feasible for Ellis’s problem if and only if it is feasible for the knapsack instance. Now, we observe that for any nonempty $\mathcal{X}$,
\else
$U_{\mathrm{max}} = \sum_{j \in \mathcal{B}} u_j$와 $\delta = {1} /{m U_{\mathrm{max}}} \in (0, 1)$일 때, $\mathcal{C} = \mathcal{B}$, $H = W$,  모든 $f_j = \delta$, 그리고 각 $t_j = u_j / \delta$인 엘리스 문제의 인스턴스를 고려하자. $\mathcal{X} \subseteq \mathcal{C}$가 엘리스 문제의 가능해가 되는 것은 배낭 문제 인스턴스의 가능해가 되는 것과 동치임을 쉽게 알 수 있다. 그러면 공집합이 아닌 임의의 $\mathcal{X}$ 에 대해,
\fi
\begin{align}
\begin{split}
\sum_{j \in \mathcal{X}} u_j &=  \sum_{j \in \mathcal{X}} f_j t_j
> \sum_{j \in \mathcal{X}} \Bigl( f_j t_j \prod_{\substack{j’ \in \mathcal{X}: \\ j' > j}} (1 - f_{j’}) \Bigr)
= v(\mathcal{X}) \\
&= \sum_{j \in \mathcal{X}} \Bigl( u_j  \prod_{\substack{j’ \in \mathcal{X}: \\ j' > j}} (1 - \delta) \Bigr)
\geq (1 - \delta)^m \sum_{j \in \mathcal{X}} u_j \\
&\geq (1 - m\delta) \sum_{j \in \mathcal{X}} u_j 
\geq \sum_{j \in \mathcal{X}} u_j  - m\delta U_{\mathrm{max}}
= \sum_{j \in \mathcal{X}} u_j  - 1.
\end{split}
\end{align}
\ifen
This means that the utility of an application portfolio $\mathcal{X}$ in the corresponding knapsack instance is the smallest integer greater than $v( \mathcal{X})$. That is, $\sum_{j \in \mathcal{X}} u_j \geq U$ if and only if $v(\mathcal{X}) \geq U -1$. Taking $V = U-1$ completes the transformation and concludes the proof. 
\else
이는 지원 포트폴리오 $\mathcal{X}$가 해당 배낭 문제에서 일으키는 효용이 $v( \mathcal{X})$보다 크면서 가장 작은 정수임을 의미한다. 즉, $\sum_{j \in \mathcal{X}} u_j \geq U$가 성립할 필요충분 조건은 $v(\mathcal{X}) \geq U -1$이다. $V = U-1$으로 정의하여 변환을 완성하면 증명이 완료된다.
\fi
\end{proof}
